Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-07-15 Supplement.tex
Commented out unused packages. Fixes #11.
Mostly: converting pdf images to jpg images.

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage[round]{natbib}
\usepackage{caption}
\usepackage{tabularx, booktabs}
\usepackage{float, placeins}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{rotating}

@@

\newcommand{\pdet}{p^{(det)}}
\newcommand{\capt}[1]{Caterpillar plots of posterior parameter estimates from all models fit to the simulated #1 dataset (from simulations involving covariates and random effects).  Black and orange lines depict central 95\% and 50\% credible intervals, respectively.  The black dot is the posterior meadian.  The blue 'X' is the true parameter value and is positioned on the correctly specified model.  $\beta$'s are fixed effect parameters, $\sigma$'s are random effect standard deviations, and $\gamma$ is a mixing parameter.  Parameters designated with an 'A' are abundance parameters; those designated with a 'D' are detection parameters.}
\newcommand{\sfig}[2]{\begin{figure}
  \includegraphics[width=1.0\textwidth, page=#2]{Sims/SimFull/Posteriors_all_simdat.pdf}
  \caption{\capt{#1}}
  \end{figure}
}
\renewcommand{\thesection}{S-\arabic{section}}   % Label section with 'S-#'
\renewcommand{\thetable}{S-\arabic{table}}
\renewcommand{\thefigure}{S-\arabic{figure}}

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family.pdf}
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

>>>>

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{parskip}
%\usepackage[round]{natbib}
%\usepackage{caption}
%\usepackage{tabularx, booktabs}
%\usepackage{float}
\usepackage{placeins}     % Enables \FloatBarrier, which enforces a break between table/figures
%\usepackage{adjustbox}
\usepackage{multirow}     % Allows tables with vertically merged cells
%\usepackage{setspace}
%\usepackage{url}
\usepackage{xr}    % Links to external document
%\usepackage{listings}
%\usepackage{verbatim}
%\usepackage{graphicx}
\usepackage{rotating}     % For landscape-oriented table

@@

\newcommand{\pdet}{p^{(det)}}
% Plug-in caption for figures created using \sfig
\newcommand{\capt}[1]{Caterpillar plots of posterior parameter estimates from all models fit to the simulated #1 dataset (from simulations involving covariates and random effects).  Black and orange lines depict central 95\% and 50\% credible intervals, respectively.  The black dot is the posterior meadian.  The blue 'X' is the true parameter value and is positioned on the correctly specified model.  $\beta$'s are fixed effect parameters, $\sigma$'s are random effect standard deviations, and $\gamma$ is a mixing parameter.  Parameters designated with an 'A' are abundance parameters; those designated with a 'D' are detection parameters.}
% Include graphics for posterior estimates of dataset parameters
\newcommand{\sfig}[2]{\begin{figure}
  \includegraphics[width=1.0\textwidth]{Sims/SimFull/Posteriors_all_simdat#2.jpg} % Source file: Sims/SimFull/Outputs_Code_sf.R
  \caption{\capt{#1}}
  \end{figure}
}
\renewcommand{\thesection}{S-\arabic{section}}   % Label section with 'S-#'
\renewcommand{\thetable}{S-\arabic{table}}
\renewcommand{\thefigure}{S-\arabic{figure}}

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family} % Source file: Sims/SimFull/Outputs_Code_sf.R
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}
